One-step, three-factor authentication with in-ear EEG

### 2016-12-05 paper.tex
some minor edits

Toward this end, propose to build a working, real-time passthought authenticator.
After performing an initial calibration setup, similar to our pilot study's protocol, above,
we will send subjects home with their custom-fit ear EEG, and ask them to use the device to authenticate
two to three times a day for a week.
(We may ask subjects to set a recurring event on their calendar to remind them, 
or pay subjects in accordances with how frequently they authenticated, up to some reasonable maximum).
After a week, subjects will return to the lab to return their equipment, debrief about their experience, and recieve payment. We will use this opportunity to walk subjects through a relatively detailed post-interview,
during which we will focus on their experiences with the device (things they may not have posted to others on the platform).

The goal of this work is to understand both the technical issues facing ear-EEG authentication
(Does the system work reliably? When and why does it fail?), and the usability issues
(How do subjects feel about having an EEG device in their ear throughout the day?).
Finally, this closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine
co-adapt during multiple authentication attempts.

After testing that our system can reliably provide authentication with a 
a secret passthought (knowledge) and unique EEG signal (inherence),
we will turn our attention to the final, third factor: posession
(of the unique, custom-fit ear EEG device).
We propose to cryptographically assure device posession
by assigning each custom-fit electrode a unique public/private keypair. 
User accounts could be associated with an earpiece's public key,
and authentication attempts from the earpiece could be signed its
its private key, producing authentication attempts that are not
forgeable by other custom-fit earpieces.

>>>>

\subsection{Evaluating a Closed-loop Passthought Authenticator}
Toward this end, propose to build a working, real-time passthought authenticator.
After performing an initial calibration setup, similar to our pilot study's protocol, above,
we will send subjects home with their custom-fit ear EEG, and ask them to use the device to authenticate
two to three times a day for a week.
(We may ask subjects to set a recurring event on their calendar to remind them, 
or pay subjects in accordances with how frequently they authenticated, up to some reasonable maximum).

After a week, subjects will return to the lab to return their equipment, debrief about their experience, and recieve payment. We will use this opportunity to walk subjects through a relatively detailed post-interview,
during which we will focus on their experiences with the device. 
The goal of this work is to understand both the technical issues facing ear-EEG authentication
(Does the system work reliably? When and why does it fail?), and the usability issues
(How do subjects feel about having an EEG device in their ear throughout the day?).
Finally, this closed-loop BCI system could help us understand how learning effects
on the human side might impact authentication performance, as the human and machine
co-adapt during multiple authentication attempts.

\subsection{Adding a Third Factor of Authentication}
After testing that our system can reliably provide authentication with a 
a secret passthought (knowledge) and unique EEG signal (inherence),
we will turn our attention to the final, third factor: posession
(of the unique, custom-fit ear EEG device).
We propose to cryptographically assure device posession
by assigning each custom-fit electrode a unique public/private keypair. 
User accounts could be associated with an earpiece's public key,
and authentication attempts from the earpiece could be signed its
its private key, producing authentication attempts that are not
forgeable by other custom-fit earpieces.
